Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-11 write_up/Supplementary.tex
Addressing reviewer comments
Figure revisions

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/habitat_spatiotemp_spp_4}
	\caption{Spatiotemporal habitat suitability - the suitability habitat
		(for Population 4) for 52 separate weeks}
	\label{fig:8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{./Plots/Matern}
	\caption{Example of different implementation of the Matern correlation
	function on autocorrelation distance}
	\label{fig:16}
\end{figure}

>>>>

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that a diagonal
		anisotropic pattern (mimicking a depth gradient) can be
		clearly seen in populations 2 and 3. The concentrated spawning
		areas are also visible in the second row of the panels
		(t=18).}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years are the light grey
		lines, the mean of all years the thick black line.}
	\label{fig:10}
\end{figure}

@@

### 2020-01-11 write_up/mixfishsim_ecolmod_revisions.tex
Figure revisions

Individual habitat preferences and thermal tolerances result in different
spatial habitat use for each population (Figure \ref{fig:9}) and consequently
different seasonal exploitation patterns (Figure \ref{fig:10}).

@@

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}). Interestingly
the largest reductions in fishing mortality happened immediately after the
closures, following which the fisheries ``adapted" to the closures \added{by
	finding new areas of high abundance to fish which led to} fishing
mortality increasing again, though not to past levels. The exception to the
success was the closures implemented based on the coarsest spatial (20 x 20)
and temporal resolution (yearly) that was ineffective (i.e. failed to reduce
fishing mortality) with all data sources. As expected, closures based on the
``known" population distribution were most effective, with differing degrees of
success using the commercial data. Fishing mortality rates on the other species
changed in different proportions, depending on whether the displaced fishing
effort moved to areas where the populations were found in greater or lesser
density. \\

@@

%% USP
Our approach is unique in that it captures fine scale population and fishery
dynamics and their interaction in a way not usually possible with real data and
thus not usually considered in fisheries simulations. While other simulation
frameworks seek to model individual vessel dynamics based on inferred dynamics
from VMS and logbook records \citep{Bastardie2010}, or as a system to identify
measures to meet particular management goals \citep{Bailey2018}, our framework
allows users to explore the assumptions in modelling observational data and
evaluate the underlying dynamics of such approaches at a fine spatial and
temporal scale.  This offers the advantage that larger scale fishery patterns
are emergent properties of the system and results can be compared to those
obtained under a statistical modelling framework. \\

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE; \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations and realising catch distributions
that may differ from the underlying populations, as identified by
\cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
populations \citep{Plaganyi2014} taking account of environmental but not
demographic stochasticity, while incorporating detailed fishing dynamics that
take account of different drivers in a mechanistic way.  \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account (Figures \ref{fig:9}, \ref{fig:mv}). \\

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{fig:9}). \\

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}deleted{)}. \\

@@

\section*{Funding} This work was supported by the MARES doctoral training
program (MARES\_14\_15) and the Centre for Environment, Fisheries and
Aquaculture Science seedcorn program (DP227AC). The authors declare no
competing interests.

@@

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/pop_dist}
	\caption{Spatial density (log abundance) for each of the four
		populations at four time steps. The darker the colour the
		greater the density of the population. Note that a diagonal
		anisotropic pattern (mimicking a depth gradient) can be
		clearly seen in populations 2 and 3. The concentrated spawning
		areas are also visible in the second row of the panels
		(t=18).}
	\label{fig:9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width = \linewidth]{Plots/f_dynamics}
	\caption{Fishing mortality dynamics - the daily fishing mortalities
		across the entire spatial domain showing weekly and seasonal
		patterns in exploitation.  Individual years a\replaced{re}{nd}
		the light grey lines, the mean of all years the thick black
		line.}
	\label{fig:10}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions
		over a ten year period. \added{The figure shows catch
			composition at each spatial unit represented by a
			square pie chart of the four populations. The area of
			each colour is proportionate to the weight of each
			population caught in that unit. Figure produced using
			the R package 'mapplots' (\cite{Gerritsen2014}.}}
	\label{fig:1}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{../analysis/f_diff_effectiveness}
	\caption{Comparison of closure scenario effectiveness based on
		different spatial and temporal resolutions.}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{The location of fishing effort before the spatial closure (a)
		and after the spatial closure (b), and the suitable habitat for
		population 3 (c). The site of the closure can be seen in the
		red box on all three panels.}
	\label{fig:17}
\end{figure}

>>>>

Individual habitat preferences and thermal tolerances result in different
spatial habitat use for each population (Figure \ref{S-fig:9}) and consequently
different seasonal exploitation patterns (Figure \ref{S-fig:10}).

@@

In most cases the fishery closure was successful in reducing fishing mortality
on the species of interest (population 3; Figure \ref{fig:3}). Interestingly
the largest reductions in fishing mortality happened immediately after the
closures, following which the fisheries ``adapted" to the closures \added{by
	finding new areas of high abundance to fish. This led to} fishing
mortality increasing again, though not to past levels (Figure \ref{fig:3}).
The exception to the success was the closures implemented based on the coarsest
spatial (20 x 20) and temporal resolution (yearly) that was ineffective (i.e.
failed to reduce fishing mortality) with all data sources. As expected,
closures based on the ``known" population distribution were most effective,
with differing degrees of success using the commercial data. Fishing mortality
rates on the other species changed in different proportions, depending on
whether the displaced fishing effort moved to areas where the populations were
found in greater or lesser density. \\

@@

%% USP
Our approach is unique in that it captures fine scale population and fishery
dynamics and their interaction in a way not usually possible with real data and
thus not usually considered in fisheries simulations. While other simulation
frameworks seek to model individual vessel dynamics based on inferred dynamics
from VMS and logbook records \citep{Bastardie2010}, or as a system to identify
measures to meet particular management goals \citep{Bailey2018}, our framework
allows users to explore \deleted{the} assumptions in modelling observational
data and \added{to} evaluate the underlying dynamics of such approaches at
\deleted{a} fine spatial and temporal scale\added{s}.  This offers the
advantage that larger scale fishery patterns are emergent properties of the
system and results can be compared to those obtained under a statistical
modelling framework. \\

%% Comparison to other models
Typically, simulation models that treat fish as individuals are focussed on
exploring the inter- and intra- specific interactions among fish populations
(e.g. OSMOSE; \cite{Shin2004}) in order to understand how they vary over space
and time. Our focus was on understanding the strengths and limitations of
inference from catch data obtained through commercial fishing activity with
fleets exploiting multiple fish populations\added{. This shows how}\deleted{
	and} realis\added{ed}\deleted{ing} catch distributions \deleted{that
}may differ from the underlying populations, as identified by
\cite{Gillis2008}. As such, we favoured a minimum realistic model of the fish
populations \citep{Plaganyi2014} taking account of environmental but not
demographic stochasticity, while incorporating detailed fishing dynamics that
take account of different drivers in a mechanistic way.  \\

@@

Our results demonstrate the importance of considering data scale and resolution
when using observational data to support management measures. We find that
understanding of the community composition dynamics will depend on the level of
data aggregation and its important to consider the scale of processes;
including population movement rates, habitat uniformity and fishing targeting
practices if potential biases in data are to be understood and taken into
account (Figures \ref{S-fig:9}, \ref{fig:mv}). \\

@@

From our simulations spatial disaggregation was more important than the
temporal disaggregation of the commercial data. This reflects the fact that
there was greater spatial heterogeneity over the spatial domain than
experienced in individual locations over the course of the year (Figure
\ref{S-fig:9}). \\

@@

We consider that the increased availability of high resolution catch and
locational information from commercial fisheries will require it to be a key
source of data for ensuring management is implemented at the right scale in
future. For example, identifying hot-spots for bycatch reduction or identifying
spatial overlaps in mixed fisheries \citep{Dolder2018, Gardner2008, Little2014,
	Dedman2015, Ward2015}. Our simulation model has the potential to test
some of the assumptions behind the modelling approaches in identifying such
hotspots and indeed behind spatiotemporal modelling in general\replaced{,}{ (}e.g. comparing
GAMs, GLMMs, Random Forests and geostatistical models under different data
generation processes as exampled by \cite{Stock2019}\deleted{)}. \\

@@

\section*{Funding and Acknowledgements} This work was supported by the MARES
doctoral training program (MARES\_14\_15) and the Centre for Environment,
Fisheries and Aquaculture Science seedcorn program (DP227AC).\added{ We thank
	two anonymous reviewers for their helpful comments which greatly
	improved the final manuscript.} The authors declare no competing
interests.

@@

@@

\begin{figure}[!ht]
	\includegraphics[width=\linewidth]{../analysis/Data_Aggregation_space_Rev2}
	\caption{[Colour] Data aggregation at different spatial resolutions
		over a ten year period. \added{The figure shows catch
			composition at each spatial unit represented by a
			square pie chart of the four populations. The area of
			each colour is proportionate to the weight of each
			population caught in that unit. Figure produced using
			the R package 'mapplots' (\cite{Gerritsen2014}.}
	}
	\label{fig:1}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width =\linewidth]{./Plots/f_diff_effectiveness}
	\caption{Comparison of closure scenario effectiveness based on
		different spatial and temporal resolutions.}
	\label{fig:4}
\end{figure}

\begin{figure}[!ht]
	\centering
	\includegraphics[width =0.5\linewidth]{./Plots/Closure_fishing_locations_yearly}
	\caption{The location of fishing effort, (a) before the spatial closure
		and (b) after the spatial closure (years in panel), and (c) the
		suitable habitat for population 3. The site of the closure
		can be seen in the red box on all three panels.}
	\label{fig:17}
\end{figure}
